Particular examples of planar integral point sets and their classification \footnote{ This work was carried out at Voronezh State University and supported by the Russian Science Foundation grant 19-11-00197. }

### 2025-11-16 AvdMomZvolA_examples/ips_examples.tex
Switch back to biblatex2bibitem
[AMZA] Cite 2407.08121 as in print

%\usepackage[backend=biber,style=gost-numeric,sorting=none]{biblatex}
%\addbibresource{../common/notmy.bib}
%\addbibresource{../common/my.bib}
%\usepackage{../../../biblatex2bibitem/biblatex2bibitem}

\usepackage{hyperref}
\usepackage{cite}

@@

While the minimal possible diameter for planar integral point sets of given cardinality was being computed,
it was noticed~\cite{kurz2008minimum} that such diameter is attained at sets with many points on a straight line;
for some estimations on this tendency, we also refer the reader to~\cite{solymosi2003note}.
Thus, the following classification was introduced:
\begin{dfn}
	A PIPS $M$ is said to be in \emph{semi-general position}
	if no three points of $M$ are located in a straight line.
\end{dfn}

@@

%\printbibliography
%\printbibitembibliography

>>>>

\usepackage[backend=biber,style=gost-numeric,sorting=none]{biblatex}
\addbibresource{../common/notmy.bib}
\addbibresource{../common/my.bib}
\usepackage{../../../biblatex2bibitem/biblatex2bibitem}

\usepackage{hyperref}
%\usepackage{cite}

@@

While the minimal possible diameter for planar integral point sets of given cardinality was being computed,
it was noticed~\cite{kurz2008minimum} that such diameter is attained at sets with many points on a straight line;
for some estimations on this tendency, we also refer the reader to~\cite{solymosi2003note};
(For the recently established connection between the characteristic and minimal possible diameter,
see~\cite{avdeev-lushina2025australas}.)
Thus, the following classification was introduced:
\begin{dfn}
	A PIPS $M$ is said to be in \emph{semi-general position}
	if no three points of $M$ are located in a straight line.
\end{dfn}

@@

\printbibliography
\printbibitembibliography
